---
title: "log"
output:   
  md_document:
    variant: markdown_github
bibliography: ../manuscript/manuscript/asreview.bib
---

This directory contains all steps taken in hyperparameter optimization and simulating automated systematic reviews. 

```{r, include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
source("R/functions.R")
knitr::opts_chunk$set(echo = FALSE)
```

# Models 
We are simulating 7 models on 6 systematic review datasets. Each model has an abbreviation to ease the programming process: 
```{r, eval = FALSE}
#  
# source("R/00_condition_grid.R")
# source("R/01_hyperparameter_sets.R")

conditiongrid <- readRDS("R/00_conditiongrid.RDS")

conditiongrid[c(1:4, 7:9),] %>%
  mutate(Model = c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )) %>%
  mutate(Abbreviation = condition) %>%
  select(Model, Abbreviation)
  kable(format = "markdown")
```
The first letter denotes the classification strategy, NB, LR, RF, or SVM. The second letter stands for C of certainty sampling. The third letter denotes the feature extraction strategy, TF-IDF or Doc2vec. The fourth letter stands for D of Dynamic Resampling. 


# Requirements 
This study requires having several packages installed, like ASReview version 0.9.3 [@ASReview2020]. 
All these requirements are listed in the `requirements.txt` file. Assuming you have Python 3.7 or higher, you can run the following to install all requirements: 
```{bash, eval = FALSE}
pip install -r requirements.txt
```


### Version information
Personal device: macos catalina 10.15.2
Cartesius supercomputer 
asreview simulation branch reorganization. 

# References