`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 

<!--
If you feel it necessary to include an appendix, it goes here.
-->


# The First Appendix

This first appendix includes all of the R chunks of code that were hidden throughout the document (using the `include = FALSE` chunk tag) to help with readibility and/or setup.

**In the main Rmd file**

```{r ref.label='include_packages', results='hide', echo = TRUE}
```

**In Chapter \@ref(ref-labels):**

```{r ref.label='include_packages_2', results='hide', echo = TRUE}
```

# List of definitions

Epoch
:  A particular 

Model. 

:   The prediction model for Active learning 

        { some code, part of Definition 2 }

    Third paragraph of definition 2.
    
Query Strategy
:   def

        { some code, part of Definition 2 }
        
        add paragraph here

    Uncertainty sampling.
    :  Selects the least sure instances for labelling. 
    
    Maximum sampling.
    :  Selects the samples with the highest prediction probability.
    
    Random and maximum sampling. 
    :  Combination of random and maximum sampling. By default samples the 95% of the instances with max sampling, and 5% of the samples with random sampling.
    

Feature Extraction Strategy
:   Feature Extraction Strategy

        { some code, part of Definition x }

    Third paragraph of definition x.
    
    Doc2Vec
    :  
    
    
    Term frequency-inverse document frequency (tf-idf)
    :   
    
    sbert
    
