---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
template <- data.frame(search = rep(0,4), # papers obtained in systematic search
                       ftext = rep(0, 4), # number of abstract inclusions
                       incl = rep(0,4), # papers included in systematic review
                       row.names = c("paper", # numbers reported in the publication
                                     "raw", # numbers published on raw dataset
                                     "asreview",
                                     "test")) # numbers in test dataset asreview

# function to compute descriptives from dataset
data_descr <- function(data){
  return(c(nrow(data), # all papers obtained in the systematic search
           sum(data$inclusion_code > 0), # number of abstract inclusions
           sum(data$included))) # papers included in systematic review
}
```

This notebook processes all five systematic review datasets into datasets that can be used for testing asreview. 

## ace dataset 
## nudging dataset 
```{r}
# by Rosanna Nagtegaal
nudging <- template
nudging["paper", ] <- c(2006, 377, 100) 
```


## PTSD dataset
```{r}
ptsd <- template 
ptsd["paper", ] <- c(6185, 363, 34) # from flowchart 

# raw --------------------------------------------------------------------------
ptsd["raw", ] 

```

```{r}
# asreview ---------------------------------------------------------------------
ptsd_asr <- read.csv("https://raw.github.com/asreview/systematic-review-datasets/master/datasets/Van_de_Schoot_PTSD/output/PTSD_VandeSchoot_18.csv",
                     header=T)

ptsd["asreview", ] <- data_descr(ptsd_asr)
```

Now, remove duplicate entries and empty abstracts to arrive at test set. 
```{r}
ptsd_test <- ptsd_asr %>%
  drop_na(abstract) %>% # drop entries with missing abstracts
  distinct(abstract, .keep_all = TRUE)# remove entries with duplicate abstracts
``` 

There are 38 inclusions in this dataset, should be 34. 
Een vraag! De 'bayesian PTSD-trajectory analysis' kent 34 final inclusions. 
Voor (het quALITS paper dan, denk ik?) 38 inclusies waren. 
```{r}
# get rid of 4 extra inclusions (see log book)
drop_id <- 
  ptsd_test %>%
  filter(included == 1, 
         str_detect(authors, "Sterling, M., Hendrikz, J., Kenardy, J.") |
         str_detect(authors, "Hou") |
         str_detect(authors, "Mason") |
         str_detect(authors, "Pérez")) %>%
  select(id)
drop_id <- drop_id$id

ptsd_test <- ptsd_test[!(ptsd_test$id %in% drop_id), ] 

```

Save the test dataset.
```{r}
# save test file
write.csv(ptsd_test %>%
            select(authors, title, abstract, included, inclusion_code), # select relevant columns
          "test_datasets/ptsd.csv")
```

Derive statistics in final test set.
```{r}
ptsd["test", ] <- data_descr(ptsd_test)
```

## software

## wilson

# Save descriptive statistics 

```{r eval = FALSE}
# put everything together in list. 
all <- list(ace = ace,
            nudging = nudging,
            ptsd = ptsd,
            software = software,
            wilson = wilson)

# save datafile, to serve as data for descriptive table in manuscript
save(all, file = "../manuscript/drafts/data/datasets_table.Rdata")
```

